EinsteinPy: Python for General Relativity\footnote{Released on January, 8th, 2018}

### 2019-07-10 paper.tex
some changes

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

@@

It was the time of 1915 when Einstein published his paper on general theory of relativity which proposed a elegant and rigorous framework for a relativistic theory of gravity and was generalized version of gravity free theory - special relativity which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted in the beginning because all people were worried that if these hypothesis true would then completely change our notion of how we percieve space and time. But sooner they started to realize the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature. After so many years its well established now that general theory of relativity is the "theory of gravity" in classical regime and all the attempts to formulate quantum theory of gravity one way or the other borrow ideas from GR. The central problem then and now remains to be the solutions of the Einstein's field equation. Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even be solved analytically for highly unrealistic systems but for solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations. This question is so profound that it has a separate research field which goes with the name of numerical relativity which attempts to use computer programmes to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics is happening (as we can not solve for a infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
The interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining. After so many years the field of numerical relativity has grown up to be a mature research area with vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones). Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher. Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demands heavy use of high level programming
in languages like C and C++. As described above Python provides a vast room for abstractions and no library existed at that time that do numerical relativity in Python and hence the team was hooked by this very fact of need for a python library on general relativity. Since then EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions. Like any other numerical relativity library EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to dive deep into the nitty gitties of the subject along with few very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity in general\footnote{More details on this are given in further coming sections}. In further coming section we will discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming version. Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
\section{Manuscript styles} \label{sec:style}

>>>>

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.
\begin{document}

@@

It was the time of 1915 when Einstein published his paper on general theory of relativity which proposed a elegant and rigorous framework for a relativistic theory of gravity and was generalized version of gravity free theory - special relativity which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted in the beginning because all people were worried that if these hypothesis true would then completely change our notion of how we percieve space and time. But sooner they started to realize the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature. After so many years its well established now that general theory of relativity is the "theory of gravity" in classical regime and all the attempts to formulate quantum theory of gravity one way or the other borrow ideas from GR. The central problem then and now remains to be the solutions of the Einstein's field equation. Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations. This question is so profound that it has a separate research field which goes with the name of numerical relativity which attempts to use computer programmes to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics is happening (as we can not solve for a infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
The interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining. After so many years the field of numerical relativity has grown up to be a mature research area with vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones). Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to an be essential tools for any numerical relativity researcher. Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demand heavy use of high level programming languages like C and C++. As described above Python provides a vast room for abstractions and no library existed at that time that do numerical relativity in Python and hence the team was hooked by this very fact of need for a python library on general relativity. Since then EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions. Like any other numerical relativity library EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to dive deep into the nitty gitties of the subject along with few very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity in general\footnote{More details on this are given in further coming sections}. In further coming section we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions. Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
\section{Data Types} \label{sec:style}
The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems. The most important and central quantity in all of the general relativity is the metric tensor which defines the background geometry of spacetime on which all the dynamics happen. EinsteinPy provides class metric
\subsection{metric}
\subsection{plotting}
\subsection{symbolic}
\subsection{coordinates}
\subsection{hypersurface}
